---
title: "Udacity HW#4"
output: html_document
---



```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
# Finds and retireves the elction data
EData <- read.csv("~/Udacity HW 4/Election_Data_Edited.csv")

library("ggplot2")

```





###Descriptive Univariate Graphs


I first created a barchart showing the amount raised by each candiate to get a sense of the data. This was a fairly easy graph to make and shows you one of the reasons why Hilary Clinton is the favorite to win the election. It shows her dominating the rest of the field with over $60,000,000 raised. The next closet is Jeb Bush with over $20 Milllion raised. 

It gave me a warning message that the stacking was not well defined when ymin does not equal 0, but the totals added up to my test calculations with excel so I decided to trust it. 


```{r TotalRecievedBar, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}

p <- ggplot(data = EData, aes(x = cand_nm, y = contb_receipt_amt)) 
q<-theme(text=element_text(size=13),axis.text.x=element_text(angle=90,vjust=1))
p + q + geom_bar(stat = "identity") 

```

A summary of the total contriubtion. Note that Hilary's Total is 20 x the median. 
```{r, echo=FALSE}
# Creates an aggregate list of the total amount contributed to each candidate
Ed <-aggregate(EData$contb_receipt_amt,by=list(Category=EData$cand_nm),FUN=sum)

summary(Ed)[8:13]

```
Below is a histogram of the data again showing frequency of Total contriubtions. AS we can see, the data is skewed far to the left. Hilary is the bar on the far right. 

```{r Hist, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}

TotalContributionsHist<- Ed$x
hist(TotalContributionsHist, breaks = 42)
```

I created another Histogram without Hilary. The data is less skewed, but there is still not a normal shape to the data. 
```{r noHilHist, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}

TotalContributionsHist<- subset(Ed, x < 6000000)$x
hist(TotalContributionsHist, breaks = 12)


```



Then I made another bar graph but did it per state, unsurprisingly California is in the lead as California has the largest total population. Followed by Texas, then New york. 

```{r StateBar, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/', fig.width = 13}

p<- ggplot(data = EData, aes(x = contbr_st, y = contb_receipt_amt))

p + q + geom_bar(stat = "identity") 
 

```





### Cumulative Sum over Time Graphs




I decided to look into the cumulative sum of the candidates contributions to see if I could find anything interesting. My first graph looks at Hilary alone. Hilary shows steady increase in funds, there are no huge leaps or flat areas which are immediately obvious.  


```{r HilOverTime, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/', fig.width=12}
   library(scales)
#Edata column showing when contriubiton is made
ContrbRcpDt <- EData$contb_receipt_dt
#Edata column showing how large the contribution is
ContrbRcpAmt <- EData$contb_receipt_amt
#Formats ContrbRcpDt in proper data format
ThruSep2015<-as.Date(ContrbRcpDt,format="%m/%d/%Y")
#Creates a data frame shoing the date, the amount and the name of the receiving candidate
CandDF =data.frame(Date =ThruSep2015,Amount=ContrbRcpAmt,Name=EData$cand_nm)
# trnasforms the data to include the names and the cumulative sum of contributions for every individual contriubitons
TrsCDF <- transform(CandDF, cumsum = ave(Amount, Name, FUN = cumsum))
#A Subset of the TrsCDF Data frame which only includes Hilary
hil <- TrsCDF[TrsCDF$Name == "Clinton, Hillary Rodham" ,]

#creates a line plot charting Hilary's cumulative amount received
a <-ggplot(data = hil, aes(x= Date , y= cumsum/1000000, colour = Name)) 
LMVar <- c(as.Date("2015-01-01"),as.Date("2015-09-30"))
b<-scale_x_date(breaks=(by=("months")),limits=LMVar,labels=date_format("%b")) 
c<- labs(title = "Total $ Recieved for Hilary Clinton  by Date") 
d <- xlab("January - October 2015")
e <- ylab("Total Recieved in Millions")
a +b +c+d +e + geom_line(size = 1)
```

Here is the graph of the top 8 candidates over time. Interestingly there is not much of an obvious distinction between the candidates trends.  

```{r top8, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
   library(scales)
#The candidate name column of TrsCDF
trf <- TrsCDF$Name

hi <-  "Clinton, Hillary Rodham"
be<- "Sanders, Bernard" 
cr <- "Cruz, Rafael Edward 'Ted'"
je <- "Bush, Jeb"
wa <- "Walker, Scott"
ca <- "Carson, Benjamin S."
ru <- "Rubio, Marco" 
fi <- "Fiorina, Carly"

# A subset of the TrsCDF which includes the top 8 candidates by total contribution amount
top8<-TrsCDF[trf==hi|trf==be|trf==cr|trf==je|trf==wa|trf==ca|trf==ru|trf==fi,]
 
# creates a line chart of the top 8 candidates cumulative sum over time. 
a <-ggplot(data = top8, aes(x= Date , y= cumsum/1000000, colour = Name))
c<-labs(title = "Total $ Recieved for Top 8 Candidates by Date") 

a+b+c+d + e + geom_line(size = 1) 
```





###Retired Contributions Analysis Graphs




This graph shows retired contribtions per candidate. Hilary is again in the lead. However, it is important to note that she also has the highest total contribution amount, so she might not have the highest proportion of retired contriubtions.  

```{r RetiredBar, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
# Creates a subset of the elction data where everyone is retired
df1 <- subset(EData, contbr_occupation == 'RETIRED')
# Creates a list of the Total amount Contributed for each candidate from retired people
df2<- aggregate(df1$contb_receipt_amt, by=list(Category=df1$cand_nm), FUN=sum) 
# Creates a column on the df2 dataframe for the percent of total contributions that are from retired persons for each candidate
df2$percent <- df2$x/Ed$x



p<-ggplot(data = df2, aes(x = Category, y = x))
z <- labs(title = "Poritons of Total $ Contributions From Retired Persons")
p +q+z +geom_bar(stat = "identity") + xlab("") + ylab("")

```

This graph shows the portion of retired persons who make up their total contriubtion base. Ben Carson has the highest portion with almost 30% of his contributions coming from retired persons. Donald Trump and Carly Fiorina are next at above 25% of the total contriubtions coming from retired persons

```{r RetiredBarPercent, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
 
 
 
p<- ggplot(data = df2, aes(x = Category, y = percent)) 
p + q + z+ geom_bar(stat = "identity") + xlab("") + ylab("")

```


I want to test whether there is a relationship between the percent of income from retired persons and Total_contriubtions. To do this I make a scatter plot with Total contriubtions and a regression line. 

```{r RetiredScatter, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
# This Adds the total contributions per candidate to the df2 data frame
df2$Total_Contributions <- Ed$x
   
p <- ggplot(df2, aes( percent, Total_Contributions)) + geom_point(size = 3)
p + geom_point(size = 3) + geom_abline(intercept= 8893144,slope= -6291339)
```


Here is the Summary of the correlation. As we can see the RSquared value is .001371477 which is very weak.

```{r, echo=FALSE}

DCCorr.lm <- lm(Total_Contributions ~ percent, data =df2)
summary(DCCorr.lm)

```



Hilary dominates the total, so lets try this again with Hilary removed.


 
```{r RetiredNohilScatter, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
# Subsets the data for only those candidates with less then $60 Million(Everyone except Hilary)
noHilSub <- subset(df2, Total_Contributions < 60000000)
p <- ggplot(noHilSub, aes( percent, Total_Contributions))
p +geom_point(size = 3) + geom_abline(intercept=2434828,slope= 19594068)
```

The line is fairly flat and the data is spread out. It doesn't look like there is a strong relationship between the portion of money that comes from retired persons and overall contributions.  The summary for the regression is below. 


```{r, echo=FALSE}
DCCorr.lm <- lm(Total_Contributions ~ percent, data =noHilSub)
summary(DCCorr.lm)

```





###Location Influence Analysis




first I want to study Washington D.C's influence on the election.
Like the retired plot I made a bar graph showing the percent of contirubtion total which comes from Washington D.C

```{r DCBar, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
#Subsets the Data for only the contributions from people living in Washington DC
DCDF <- subset(EData, contbr_st == 'DC')

#Aggegrates the data into a data frame showing th total amount recieved per candidate from people living in DC
DCDF2<-aggregate(DCDF$contb_receipt_amt,by=list(Category=DCDF$cand_nm),FUN=sum)

#Each candidates name once
CandNM <- unique(EData$cand_nm)

# Adds in the Candidates who did not get any contriubtions from DC with a value of 0 
notIn <- subset(CandNM, !(CandNM %in% DCDF2$Category))
     for(j in notIn) {
       newRow = c(j,0)
       DCDF2 = rbind(DCDF2, newRow)}
#order the candidate names and change the values to numeric values
DCDF2 <- with(DCDF2, DCDF2[order(Category, x),])
DCDF2$x <-as.numeric(DCDF2$x)

#Adds in the total contributions, including those outside of DC to DCDF2
DCDF2$Total_Contributions <- Ed$x

#Adds in the percent of Total Contriubtions that are from Washington DC to DCDF2
DCDF2$percent <- DCDF2$x/Ed$x
p <-ggplot(data = DCDF2, aes(x = Category, y = percent)) 


z<- labs(title = "Poritons of Total $ Contributions From Wahington DC") 
p +q +z+ xlab("") + ylab("") + geom_bar(stat = "identity")

#
```

I created a graph that looks at the percent of contributions from DC with the total donations overall

```{r DCScatter, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
p <- ggplot(DCDF2, aes( percent, Total_Contributions))
p+geom_point(size = 3)+geom_abline(intercept=-88231.64,slope = 677052822.47)

```

There looks to be a stronger correlation with percent of contriubtions from Washignton DC then with retired persons, with every extra .01 % from Washington DC leading to an expected increase of around $7M in total contributions. The R Squared here is not too high:

```{r DCCorrchart, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
DCCorr.lm <- lm(Total_Contributions ~ percent, data = DCDF2)
summary(DCCorr.lm)$r.squared 

```
But is not weak enough to be dicounted completely. I think it is fairly likely that percent of contriubtions coming from Wahington DC are likely to predict larger total contributions.



Now I will try to see DC's influence compared with  States and Cities. First, here is a scatter plot showing what percent of each candidates money comes from every state. For instance, 60% of Chris Christie's money comes from his native New Jersey, as indicated by the larger dot. I limited the data to state values which make over 1.5% of the value for that candidate to help filter out the less relevant variables. 

```{r StateDot, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/', fig.width=10}
# Constructs a dataframe with all the percentiles of Total_contribution for each candidate for each state
States <- unique(EData$contbr_st)

#Creates a data Frame with the names of the candidates once
SuperStateDF <- data.frame(DCDF2$Category)

#This funtion loops through the states and eventually creates a Data Frame showing what percentile of their total contributions that candidates get per state
 for(i in States){
   #Subsets the Edata dataframe for every state
     StateDF <- subset(EData, contbr_st == i)
   #creates a data frame consisting of the candidate names in the above StateDF
     CV <- StateDF$cand_nm
   #creates a dataFrame consisting of the contriubtion amounts in respective StateDF
     CRA <-StateDF$contb_receipt_amt
   #Creates a dataframe from StateDF which contains the amount contributed per candidate in the respective state
     StateDF2<-aggregate(CRA,by=list(Category=CV),FUN=sum)
  #A dataframe consisting of the candidates that did not receive any contributions from the state 
     notIn <- subset(CandNM, !(CandNM %in% StateDF2$Category))
  #Adds in the candidates without contriubitons into the StateDF2 dataframe with a value of 0   
     for(j in notIn) {
       newRow = c(j,0)
       StateDF2 = rbind(StateDF2, newRow)
       
     }
     #Orders the candidate column by name and changes the conribution values to numeric
     StateDF2 <- with(StateDF2, StateDF2[order(Category, x),])
     StateDF2$x <-as.numeric(StateDF2$x)
     #Creates a dataframe with the states as the column names and the candidates as the values of the first column. The percentiles of each state er candidate make up the rest of the rows
     SuperStateDF[[paste(i)]] <- StateDF2$x/Ed$x
     
 }
#creates an empyty data frame 
SuperStateDF2 <- data.frame(State=factor(),
                            Cand_NM=factor(),
                            Perc_Cand_State =numeric())

#adds in the values of the SuperStateDF2 into the empty data frame
for (i in States){
  
  countVar = 0
  
  for(j in unique(SuperStateDF$DCDF2.Category)) {
  
  countVar =  countVar + 1
  percentValue <- SuperStateDF[countVar, i]
  newDF=data.frame(State=c(i),Cand_NM=c(j),Perc_Cand_State=c(percentValue))
  #binds each row containg the name of the State, the name of the candidate and the total percentile of contributions that went to the candidate from the state. 
  SuperStateDF2 <- rbind(SuperStateDF2, newDF)}
  
  }



p <- ggplot(subset(SuperStateDF2,Perc_Cand_State>.015),aes(x=State,y=Cand_NM))
SDL<-labs(title = "Percent Candidates Receive per State") 
x <- xlab("Candidate Name")
scale <- scale_size_continuous(range=c(2, 4), guide = guide_legend(title = "Percent Recieved Size")) 
p+q+ SDL + scale + geom_point(aes(size=Perc_Cand_State))


```

Here we can see that the DC area is by far the most influential State/Region which would make sense as it is the center of politics in the United States, and someone with the support of those with money in DC would likely have connections to donors all over the country. I limited the values shown to RSquared values over .05.


```{r R2State, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
#Creates empty data frame
rSquaredDF <- data.frame(State=factor(),
                            RSquared=numeric())
#Adds in  the r squared value of the correlation between the percentile each canidate recieved from the state and the total contributions to each candidate, to the rSquaredDF.
for(i in States){
  
  
  DCCorr.lm<-lm(Perc_Cand_State~Ed$x,data=subset(SuperStateDF2,State==i))
  #aquires the RSquared Score
  r2Score<-summary(DCCorr.lm)$r.squared  
  RRowDF<-data.frame(State=c(i),RSquared=c(r2Score))
  rSquaredDF <- rbind(RRowDF, rSquaredDF)
}

p<-ggplot(subset(rSquaredDF,RSquared > .05 ), aes( x = State, y = RSquared))
p  + geom_bar(stat = "identity")

         
       
```





However, DC is a city as well as a district, so influence is more concentrated then with States.  Below is a graph showing which Cities give to which candidates.  For simplicity and processing, I limited the cities to the top 75 cities by number of donations. Also, like with the states, I limited the threshold of the data to cities which are over 1.5% of any candidates total contributions. 


```{r CityDot, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/', fig.width=10}

Cities <- tail(names(sort(table(EData$contbr_city))), 75)
CandNM <- unique(EData$cand_nm)

# Creates a Data Frame with the cities as the column names past row one. The Candidate Names are the first column and the percent of Total contriubtions from the respective city attributed to each candidate in the columns afterwards

SuperCDF<-data.frame(DCDF2$Category)
 for(i in Cities){
    # Creates a subset of the data for each city
     CDF<-subset(EData, contbr_city == i)
     CDF_Amount <- CDF$contb_receipt_amt
     #Aggregates the total each candidate receives from the respective city
     CDF2<-aggregate(CDF_Amount,by=list(Category=CDF$cand_nm),FUN=sum)
     
     #If the candidate does not recieve any money from the city, this chunk adds in the
     #candidate and assigns him or her a value of 0
     notIn<-subset(CandNM,!(CandNM %in% CDF2$Category))
     for(j in notIn) {
       
       newRow=c(j,0)
       CDF2=rbind(CDF2,newRow)
       
     }
     #Orders the row by the Candidate name and makes the contrbution column numeric
     CDF2 <- with(CDF2, CDF2[order(Category, x),])
     CDF2$x <-as.numeric(CDF2$x)
     
     #Adds on the the column for each city with percent of total contriubtions due from each city
     SuperCDF[[paste(i)]] <- CDF2$x/Ed$x
     
 }
#Creates empty dataframe

SuperCDF2 <- data.frame(City=factor(),
                            Cand_NM=factor(),
                            perc_cand_city =numeric())

#This funtion loops through the cities and creates a Data Frame showing what percentile of their total contributions that candidates get per City
for (i in Cities){
  countVar = 0
  for(j in unique(SuperCDF$DCDF2.Category)) {
  countVar=countVar + 1
  
  # Gets the percent of the Total Value for a candidate which is from the respective city
  percentValue<-SuperCDF[countVar, i]
  
  newDF=data.frame(City=c(i),Cand_NM=c(j),perc_cand_city=c(percentValue))
  #Adds in the percentage of total contributions from each repsective city per candidate
  SuperCDF2<-rbind(SuperCDF2,newDF)}
}

p<-ggplot(subset(SuperCDF2,perc_cand_city>.015 ),aes( x=City,  y = Cand_NM))
p+q+geom_point(aes(size=perc_cand_city ))+scale_size_continuous(range=c(2,4))


```


Here is a graph of the RSquared data for each city. Washington DC still shows the highest R Squared value. Surprisingly, Mineapolis is the second highest. 

```{r R2City, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
#creates empty data frame
rSquaredDF <- data.frame(City=factor(),
                            RSquared=numeric())

#Adds in  the r squared value of the correlation between the percentile each canidate recieved from the city and the total contributions to each candidate, to the rSquaredDF.
for(i in Cities){
  
  DCCorr.lm <- lm( perc_cand_city ~ Ed$x ,data =subset(SuperCDF2,City ==i))
  r2Score <- summary(DCCorr.lm)$r.squared  
  RRowDF <- data.frame(City = c(i), RSquared = c(r2Score))
  #adds in the respective city names and rsquared values to rSquaredDF 
  rSquaredDF <- rbind(RRowDF, rSquaredDF)
}

cityp <- ggplot(subset(rSquaredDF,RSquared>.05 ), aes(x = City,y = RSquared))
r2CityLab <- labs(title = "R^2 Value of Percent ~ Total_Contriubtions per City") 
r2ylab <- ylab("Coefficient of determination")
cityp  + q + r2CityLab +geom_bar(stat = "identity") + r2ylab
      
       
```

I want to narrow down the sources of influence even further, so I will now repeat the process but with zip codes. Here is a scatter plot. I made the cut to be counted as .5% rather then 1.5% because zipcodes are smaller and naturally will make a smaller part of the Total Contributions. For some context 10024 is the Zip Code for the upper West Side in Manhattan. 77024 is a zip code in Houston, two miles away from where Ted Cruz went to High School.  

```{r ZipDot, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}

#A list of the top 100 zip codes by count
Zips <- tail(names(sort(table(EData$contbr_zip_short))), 100)


# Creates a Data Frame with the cities as the column names past row one. The Candidate Names are the first column and the percent of Total contriubtions from the respective zip-Code attributed to each candidate in the columns afterwards

SuperZDF <- data.frame(DCDF2$Category)
 for(i in Zips){
    # Creates a subset of the data for each Zip Code
     ZDF <- subset(EData, contbr_zip_short == i)
     ZDFAMOUNT <- ZDF$contb_receipt_amt
     #Aggregates the total each candidate receives from the respective Zip Code
     ZDF2<-aggregate(ZDFAMOUNT,by=list(Category=ZDF$cand_nm),FUN=sum)
     
     #If the candidate does not recieve any money from the Zip Code, this chunk adds in the
     #candidate and assigns him or her a value of 0
     notIn <- subset(CandNM,!(CandNM %in% ZDF2$Category))
     for(j in notIn) {
       
       newRow = c(j,0)
       ZDF2 = rbind(ZDF2, newRow)
       
     }
     #Orders the row by the Candidate name and makes the contrbution column numeric
     ZDF2 <- with(ZDF2, ZDF2[order(Category, x),])
     ZDF2$x <-as.numeric(ZDF2$x)
     
     #Adds on the the column for each city with percent of total contriubtions due from each Zip Code
     SuperZDF[[paste(i)]] <- ZDF2$x/Ed$x
     
 }
#creates empty data frame
SuperZDF2 <- data.frame(Zip=factor(),
                            Cand_NM=factor(),
                            Zip_Per_Cand =numeric())
#This funtion loops through the cities and creates a Data Frame showing what percentile of their total contributions that candidates get per Zip Code
for (i in Zips){
  countVar = 0
  for(j in unique(SuperZDF$DCDF2.Category)) {
  countVar =  countVar + 1
  
  # Gets the percent of the Total Value for a candidate which is from the respective city
  percentValue <- SuperZDF[countVar, i]
  
  newDF = data.frame(Zip = c(i),Cand_NM = c(j),Zip_Per_Cand= c(percentValue))
  
  SuperZDF2 <- rbind(SuperZDF2, newDF)}
}

p <-ggplot(subset(SuperZDF2, Zip_Per_Cand >.015 ),aes(x = Zip,y = Cand_NM))
y <- scale_size_continuous(range = c(2, 4))
p +q + y + geom_point(aes(size = Zip_Per_Cand ))

```



Here are the r-scores of the top districts in terms of influence. The results are much more siginificant then the city or state data, with the top r^2 value reacing over .7. For context, the top score, zip code: 60614 is the Lincoln Park area of Chicago and which contains Dupont University. 20009 is a zip Code minutes near the Washington DC Mall. 90046 is the Zip Code for West Hollywood and the Hollywood hills, 90069 is the zip code right next door on the sunset strip. 10128, is the Zip Code for the Carneige Hill area of Manhatten. 

```{r TopR2Zips, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
#creates emptydataframe
rSquaredDF <- data.frame(Zip=factor(),
                           RSquared=numeric())
 #Adds in  the r squared value of the correlation between the percentile each canidate recieved from the Zip Code and the total contributions to each candidate, to the rSquaredDF.
for(i in Zips){
  
  
  DCCorr.lm <- lm( Zip_Per_Cand ~ Ed$x ,data = subset(SuperZDF2,Zip == i ))
  r2Score <- summary(DCCorr.lm)$r.squared  
  RRowDF <- data.frame(Zip = c(i), RSquared = c(r2Score))
  rSquaredDF <- rbind(RRowDF, rSquaredDF)
}

p <- ggplot(subset(rSquaredDF,RSquared > .1 ), aes( x = Zip,  y = RSquared))
p  + q + geom_bar(stat = "identity")
      
       
```

These places are all very wealthy, liberal and often culturally important areas.This would make sense as wealthy Democrats are more likely to live in large cities, and have their wealth concentrated into a few zip codes. Republican wealth is more likely to be spread over several zip-codes. As a result we would expect to find that the Democrats who capture these key areas are likely to have a larger overall base of financial support.   

These next two graphs show the total value of the contributions from 60614, then the portion of the candidates total that are from 60614.




```{r ChiZipBarTotals, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
ChiZipDF <- subset(EData, contbr_zip_short == '60614')
ChiZipAmt <- ChiZipDF$contb_receipt_amt
ChiZipDF2<-aggregate(ChiZipAmt,by=list(Category=ChiZipDF$cand_nm),FUN=sum)

#adds in the canidates with no contribtions from 60614
notIn <- subset(CandNM, !(CandNM %in% ChiZipDF2$Category))
     for(j in notIn) {
       newRow = c(j,0)
       ChiZipDF2 = rbind(ChiZipDF2, newRow)
       
     }
#orders the data-frame by name and then makes the contribution amounts numeric
ChiZipDF2 <- with(ChiZipDF2, ChiZipDF2[order(Category, x),])
ChiZipDF2$x <-as.numeric(ChiZipDF2$x)

#Adds in the total_contributions
ChiZipDF2$Total_Contributions <- Ed$x
ChiZipDF2$percent <- ChiZipDF2$x/Ed$x

p <-ggplot(data = ChiZipDF2, aes(x=Category,y=x))+geom_bar(stat ="identity") 
p + q +labs(title="Total $ Contributions From Zip 60614")+ xlab("")+ylab("")

```




```{r ChiZipBarPercent, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
p <-ggplot(data = ChiZipDF2, aes(x = Category, y = percent)) 
w<-labs(title="Portions of Total $ Contributions: Zip 60614")
x <-xlab("")
y<- ylab("")
p + q + w +x +y + geom_bar(stat = "identity") 

#
```


Here is the a scatter plot with trendlines for Zip Code 60614

```{r ChiZipScatter, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
ChiZipCorr.lm <- lm(Total_Contributions ~ percent, data =ChiZipDF2)
summary(ChiZipCorr.lm)

p <- ggplot(ChiZipDF2, aes( percent, Total_Contributions))
p +geom_point(size = 3)+geom_abline(intercept = -2.556e+04,slope =1.217e+10)



```

Here is the same graph but without Hilary, as well as a correlation summary.
```{r ChiZipNoHil, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}

#subset of the data which does not include Hilary Clinton's values
noHilSub2 <- subset(ChiZipDF2,Category != 'Clinton, Hillary Rodham')
ChiZipCorr.lm <- lm(Total_Contributions ~ percent,data = noHilSub2)
summary(ChiZipCorr.lm)

p <- ggplot(noHilSub2, aes( percent, Total_Contributions))
p + geom_point(size = 3)+geom_abline(intercept=3.410e+06,slope=3.846e+09)

```


Without Clinton, the correlation is much less strong. It would be interesting to compare this to the data in the 2004 and 2008 election and before to see if these zip codes predict the mainstream well funded Democrats(essentially only Hilary in this elction) or if they are simply very pro Hilary and would not have a strong correlation with elections not involving Hilary. 








 

#Final Plots and Summary




###Plot One:
```{r final_plot_1, fig.width=10,echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
p <- ggplot(subset(SuperStateDF2,Perc_Cand_State>.015),aes(x=State,y=Cand_NM))

p+q+ SDL + scale + geom_point(aes(size=Perc_Cand_State))
```


####Description One:
Plot one shows the percent of a candidates Total_contribution which comes from each particular state. You can see that the generally the less popular candiadtes generally have contributions coming from mostly there home state(eg. Bobby Jindal has 80% of his contributions coming from Louisianas does George Pataki % from New York). Candidates with larger total contriubitons have a more diversified base of support. For instance Hilary has significant portions of revenue (defined as over 2.5% of her total) coming from 15 states. 

Looking at the states, Florida and California are the only states to contribute over 2.5% of every candidates Total Contriubtions, which makes some sense as these states are very populous. It is interesting to note however, that both Florida and Califonia do not provide over 20% of any candidates total contributions. 



###Plot Two:

```{r final_plot_2, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
cityp  + q + r2CityLab + r2ylab +geom_bar(stat = "identity") 

```


####Description Two:
This graph shows the "Coefficient of determination" or R Squared Score betweeen  contributions for a candidate which come from that particular city, and the Total_contriubitons overall. In other words this score shows the proprtion of the differences in the Total Contributions for each candidate, which can be predicted by the percentage of Total Contriubtions each candidate gets from the respective city.

Washington DC unsurprisingly has the highest Rsquared value, which makes sense given the fact that DC has the most political power. Minneapolis is second for less clear reasons. Surprisingly New York barely makes the .05 threshold for appearing on the graph. The inclusion of Salt Lake City at a .16 value is logical as it is the center for the Mormon Faith, and would most likely be a good indicator of the contribtions of the entire Mormon community. One city that is included, Coral Gables at .15, does not make sense if you did not know it was very close suburb to Miami.

It is important to note that, below an R Squared score of roughly .4 you can not make to many determinations about the influence, as the result could be statistical noise, so discussions of influence must be taken with a grain of salt.  



###Plot Three:

```{r final_plot_3, echo=FALSE, cache=TRUE, cache.path = 'cache/', fig.path='figure/'}
a+b+c+d + e + geom_line(size = 1) 
 
```


####Description Three:

This graph shows the top 8 eight candidates by there campaign contributions over time. The jump on July 1 was due to the end of the campaign rebate program,which showed up in my data as negative total_contriubitons. This had been depressing the overall campaign contributions of many of the canidates significantly. Most notably was Jeb Bush who saw a jump of around $4 Million Dollars as a result of the rebate program. 

Also interesting is the jump that many candidates reciever (around $1-3Million each) at the end of the October. I am not sure why this is the case, but I would guess that it has something to do with the end of the fiscal year which occurs in October. Also intereting to me is the bump that Ted Cruz exeriences around the first of April. Ben Carson is the only other candidate who is active in the race at that point and he had raised very little at that point. As a result it is hard to tell whether that bump is a result of something Ted Cruz did, or something procedural. I would guess however, that is procedural phenomenon, like the end of the fiscal year bump, because it occurs exactly at the half-way point of the fiscal year. 





###Reflections:


The data provided many intriguing insights on the election and election funding. The first is that Hilary is dominating in the democratic polls for a reason. She has taken far more money in then any other candidate, and that should really help her hold off Bernie Sanders and help tremendously with the genereal election as well. 

It was also interesting that the candidates with the highest level of retired support were the three outisiders on the republican side, Carly Fiorina, Donald Trump and Ben Carson. This indicates that retired persons are likely very disastisfied with the Republican establishment, as these three candidates are not establishment republicans. 

I thought the location analysis was especially interesting. The fact that Washington DC was so influential made a lot of sense. It was interesting to see that as a whole NYC was not especially influential, but that one of it's zip-codes was. This leads me to believe that NYC has strafied locational influence zip-code to zip-code. The same is true of the LA area and the Hollywood Hills area Zip Codes. 

In the future I would like to compare the influence of location on Republicans and Democrats repsectively. I would also like to look at which jobs are the most influential, and map rSquared values as I did with location.I would also like to map the infulence of these loactions and jobs on actuall poll numbers and votes, not just overalll contriubtions.

I struggled somewhat with doing the time/date data as it was initially in the wrong format, and I had to convert it properly in order to use it. I also could not find a function that listed the Top8 candidates in the format that I wanted, meaning that I had to list them myself. It was a struggle getting that line under 80 characters. 

It is important to note that these amounts only cover the money going to the candidates themselves. The candidates also have super-pacs which they are not officially allowed to control. These superpacs are allowed to take unlimited amount of campaign contributions and as a result often have even more money then the individual campaigns. 







###Sources:
http://stackoverflow.com/questions/13540955/ggplot2-r-markdown
http://www.dummies.com/how-to/content/how-to-extract-values-from-a-matrix-in-r.html
http://www.r-tutor.com/r-introduction/data-frame
http://stackoverflow.com/questions/15285089/r-duplicate-row-names-are-not-allowed
http://flowingdata.com/2015/02/18/loading-data-and-basic-formatting-in-r/
ftp://ftp.fec.gov/FEC/Presidential_Map/2016/DATA_DICTIONARIES/CONTRIBUTOR_FORMAT.txt
http://stackoverflow.com/questions/12504549/how-to-change-the-font-size-and-color-of-x-axis-and-y-axis-label-in
http://stackoverflow.com/questions/18165578/subset-and-ggplot2
http://stackoverflow.com/questions/15210805/r-and-ggplot2-make-line-graph-of-sum-of-value-for-three-categorical
http://stackoverflow.com/questions/25086798/compute-cumulative-sum-for-levels-of-a-nesting-variable
http://www.ats.ucla.edu/stat/r/faq/subset_R.htm
http://stackoverflow.com/questions/21313905/how-to-set-ggplot-alpha-transparency-value-for-all-points-at-once
https://en.wikipedia.org/wiki/Coefficient_of_determination
http://www.r-bloggers.com/running-totals-in-r/
http://stackoverflow.com/questions/15768099/ggplot2-and-cumsum
http://stackoverflow.com/questions/1177926/r-object-identification
http://stackoverflow.com/questions/10085806/extracting-specific-columns-from-a-data-frame
http://stackoverflow.com/questions/17496358/r-help-converting-factor-to-date
http://stackoverflow.com/questions/3606697/how-to-set-limits-for-axes-in-ggplot2-r-plots
https://stat.ethz.ch/R-manual/R-devel/library/base/html/Logic.html
http://stackoverflow.com/questions/26644994/selecting-top-n-values-within-a-group-in-a-column-using-r
https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html
http://www.r-bloggers.com/installing-r-packages/
http://docs.ggplot2.org/0.9.3/geom_point.html
http://stackoverflow.com/questions/20689650/how-to-append-rows-to-an-r-data-frame
http://stackoverflow.com/questions/30446905/rmarkdown-font-size-and-header
http://stackoverflow.com/questions/21297989/sort-data-frame-column-by-factor
http://blog.datacamp.com/tutorial-on-loops-in-r/
http://stackoverflow.com/questions/13774773/check-whether-value-exist-in-one-data-frame-or-not
https://stat.ethz.ch/pipermail/r-help/2005-August/077420.html
http://stackoverflow.com/questions/7201341/how-can-2-strings-be-concatenated-in-r
http://stats.stackexchange.com/questions/2125/whats-the-difference-between-correlation-and-simple-linear-regression
http://stackoverflow.com/questions/1330989/rotating-and-spacing-axis-labels-in-ggplot2
http://rmarkdown.rstudio.com/authoring_basics.html